### 2019-07-08 papers/journal/prelim.tex
Added the rebuttal First Draft

The QBF solver adds support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.

>>>>

The QBF solver adds support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.
%
We will model the search problem for the universal condition as a QBF~\cite{buning2009theory, benedetti2008qbf}, and the resultant formula is solved using a QBF solver.
%
The QBF is a generalization of the Boolean satisfiability problem in which every variable is quantified using either existential or universal quantifier.
%
The QBFs enables potentially more succinct encodings than SAT~\cite{jussila2007compressing} although much more difficult~\cite{savitch1970relationships, stockmeyer1973word} to solve.

### 2019-07-08 papers/journal/problem.tex
Added the rebuttal First Draft

\subsection{Search for universal condition}
%
% Similarly, for the conjecture that k-connectedness is a universal condition for the VTS,
For some $k>0$,
we have to ensure that every graph of $k$-connected structure satisfies all
the rules of the system.
%
We also aim to find the minimum $k$. 
% We also have to ensure that the particular k is the least one. 
%
This condition can be specified as: for every k-connected graph, there exists a satisfiable assignment following the rules of the system. 
%
% \begin{align*}
%   & \forall G \, \texttt{Connectivity(k)} \implies  \exists
%                         f,p: \texttt{Stability} \, \land \, \texttt{Fusion}  
%   \tag{U}\label{eq:univcond}
% \end{align*}
%
We will use the same procedure as the existential condition to ensure the k to be the least one.
%
The formula for the problem has quantifier alternation. 
%
Most SAT solvers can check (at least efficiently) only quantifier-free formulas.
%
We need a QBF solver for such queries.
%
We will model the search problem for the universal condition as a QBF~\cite{buning2009theory, benedetti2008qbf}, and the resultant formula is solved using a QBF solver.
%
The QBF is a generalization of the Boolean satisfiability problem in which every variable is quantified using either existential or universal quantifier.
%
The QBFs enables potentially more succinct encodings than SAT~\cite{jussila2007compressing} although much more difficult~\cite{savitch1970relationships, stockmeyer1973word} to solve.

>>>>

\subsection{Search for universal condition}
%
% Similarly, for the conjecture that k-connectedness is a universal condition for the VTS,
For some $k>0$,
we have to ensure that every graph of $k$-connected structure satisfies all
the rules of the system.
%
We also aim to find the minimum $k$. 
% We also have to ensure that the particular k is the least one. 
%
This condition can be specified as: for every k-connected graph, there exists a satisfiable assignment following the rules of the system. 
%
% \begin{align*}
%   & \forall G \, \texttt{Connectivity(k)} \implies  \exists
%                         f,p: \texttt{Stability} \, \land \, \texttt{Fusion}  
%   \tag{U}\label{eq:univcond}
% \end{align*}
%
We will use the same procedure as the existential condition to ensure the $k$ to be the least one.
%
The formula for the problem has quantifier alternation. 
%
Most SAT solvers can check (at least efficiently) only quantifier-free formulas.
%
We need a QBF solver for such queries.
%
